Wealth dynamics in the presence of network structure and primitive cooperation

### 2019-07-08 manuscript/analysis.tex
Add effective wealth plot.

This history can be seen in Figure~\ref{fig:singleRun}. The top plot depicts
agent wealth at every iteration, and the bottom plot shows the balances of the
protos at the same points in time. (No protos exist until stage 2, by
definition.) Note that the isolates (orange lines) never form protos, and
therefore begin the starvation stage with a higher personal wealth to draw
from. We verified that changes to basic parameters have the expected effect:
lowering the initial wealth delays the onset of stage 2; a higher $\sigma^2$
for the income distribution makes the lines less jagged; a higher metabolic
rate hastens extinction; \textit{etc.}

>>>>

This history can be seen in Figure~\ref{fig:singleRun}. The top plot depicts
agent wealth at every iteration, and the bottom plot shows the balances of the
protos at the same points in time. (No protos exist until stage 2, by
definition.) Note that the isolates (orange lines) never form protos, and
therefore begin the starvation stage with a higher personal wealth to draw
from.

\begin{figure}[ht]
\centering
\includegraphics[width=\columnwidth]{figures/sampleEffectiveHistory.png}
\caption{The same simulation run as Figure~\ref{fig:singleRun}, but this time
depicting each agent's \textit{effective} wealth (its personal wealth plus its
share of its proto's wealth, if any).}
\label{fig:effectiveWealthSingleRun}
\end{figure}

Figure~\ref{fig:effectiveWealthSingleRun} shows the same information in another
way: instead of plotting each agent's \textit{personal} wealth (as in the top
plot of Figure~\ref{fig:singleRun}, we show its \textbf{effective wealth},
defined as the sum of its personal wealth and its ``share'' of its proto's
wealth (if any). After all, contributions that a proto's members make to its
balance are available to those members in times of need; therefore, a fair
comparison between isolates and non-isolates should take this into account.
From the figure, it can be seen that isolates no longer have a systematic
advantage (as they appeared to in Figure~\ref{fig:singleRun}.

We verified that changes to basic parameters all have the expected effect:
lowering the initial wealth delays the onset of stage 2; a higher $\sigma^2$
for the income distribution makes the lines less jagged; a higher metabolic
rate hastens extinction; \textit{etc.}
